Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

So, although the research tends to hold self-confidence but also entrepreneurial self-efficacy as an individual feature, we intend to understand to what extent these individual characteristics are partly shaped at a collective societal level, and more specifically through education systems and their personnel's attitudes. Indeed, in the education literature, .....

>>>>

So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems. Specifically, we wonder to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many cultural and educational parameters differ but, one stands out that is the positive reinforcement effectively in use throughout the compulsory education system in the UK. We would like to verify if this has to do with the amount of self-efficacy mentioned above.
